% !TEX root = ../main.tex

\chapter*{Daftar Pustaka}
\addcontentsline{toc}{chapter}{Daftar Pustaka}

\begin{enumerate}[label={[\arabic*]}]
    \item Vinyals, O., Toshev, A., Bengio, S., \& Erhan, D. (2015). \textit{Show and Tell: A Neural Image Caption Generator}. \url{https://arxiv.org/abs/1411.4555}

    \item Tanti, M., Gatt, A., \& Camilleri, K. P. (2017). \textit{Where to Put the Image in an Image Caption Generator}. \url{https://arxiv.org/abs/1703.09137}

    \item Selvaraju, R. R., Cogswell, M., Das, A., Vedantam, R., Parikh, D., \& Batra, D. (2016). \textit{Grad-CAM: Visual Explanations from Deep Networks via Gradient-based Localization}. \url{https://arxiv.org/abs/1610.02391}

    \item Zhang, A., Lipton, Z. C., Li, M., \& Smola, A. J. \textit{Dive into Deep Learning}. CNN and RNN/LSTM chapters. \url{https://d2l.ai}

    \item Stanford CS231n. \textit{Convolutional Neural Networks}. \url{https://cs231n.github.io/convolutional-networks/}

    \item TensorFlow Keras Documentation. \textit{Save, serialize, and export models}. \url{https://keras.io/guides/serialization_and_saving/}

    \item TensorFlow Keras API Documentation. \textit{TextVectorization}. \url{https://www.tensorflow.org/api_docs/python/tf/keras/layers/TextVectorization}

    \item TensorFlow Tutorial. \textit{Image captioning}. \url{https://www.tensorflow.org/tutorials/text/image_captioning}

    \item Kaggle. \textit{Intel Image Classification Dataset}. \url{https://www.kaggle.com/datasets/puneet6060/intel-image-classification}

    \item Kaggle. \textit{Flickr8k Dataset}. \url{https://www.kaggle.com/datasets/adityajn105/flickr8k}

    \item NumPy Developers. \textit{NumPy Documentation}. \url{https://numpy.org/doc/stable/}

    \item NLTK Documentation. \textit{BLEU and METEOR evaluation}. \url{https://www.nltk.org/api/nltk.translate.html}
\end{enumerate}
